Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-29 latex/afm-cs-main.tex
Split the metrics figures into three individuals.

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times.

@@

The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
and inpainting, in which the first term seeks a sparse solution while the
last two terms try to diffuse pixel information.
\todo{When written this way, it seems that BP+VV/TV can could also be interpreted in the frameowrk of overcomplete dictionaries?\cite{candes_redundant_2011}. }
To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}
\end{equation*}
where
\begin{equation*}
W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T.
%   W = \begin{bmatrix}U^T\\\alpha_hD_h\\\alpha_vD_v \end{bmatrix}.
\end{equation*}
One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
\begin{equation}
  f_{\mu} = \max_{u\in Q_d} \left\langle u,
    W x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
\end{equation}
The gradient of \eqref{eqn:fcn_prox} is given by
\begin{equation*}
  \nabla f_{\mu}(x)[i] = W^Tu_{\mu}(x)
\end{equation*}
where
\begin{equation*}
  (u_{\mu}(x))[i] = 
\begin{cases}
    \mu^{-1}(Wx)[i], & |W x[i]| < \mu,\\
    \text{sgn}(W x[i]), & \text{else}.
  \end{cases}
\end{equation*}
The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.
\todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
\begin{algorithm}
  \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}

@@

\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[htbp]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV} & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    % \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_framed}
    %                                & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_40mu}		
    %                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu}
    %                                                                              & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_zoomin}
    %                                                                                                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_mu40_zoomin}
    %                                                                                                                                                    & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu_zoomin}\\	
    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}	
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}	
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}	\\
    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}	
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}	
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}		
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\todo{Re-do this figure???}
\endgroup

@@

@@

All control logic is programmed using LabVIEW 2019 and compiled to a Xilinx
Spartan-6 LX150 Field Programmable Gate Array (FPGA) inside the cRIO-9082. The
cRIO includes a 16-Bit, 100 kHz NI-9215 analog-to-digital input module and a
16-Bit, 100 kHz NI-9263 digital-to-analog output module. All control loops are
implemented using a 25 kHz sampling rate.
\begin{figure}
  \includegraphics[width=1\columnwidth]{figures/exp_setup.pdf}
  \caption{Schematic diagram of the expermental AFM setup.}
  \label{fig:exp_setup}
\end{figure}
% =========================================================================
\section{Control}\label{sec:control}
The control structure for each axis is different. For the $X$-axis, we use a
state space controller. It is described fully in \cite{braker_afmmpc_2019} and
achieves a bandwidth of about 150 Hz, which is over 1/3 of the first $X$-axis
resonance at 350 Hz.

@@

For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency. We truncate this series such that the highest frequency is smaller than 200 Hz. See, e.g., \cite{clayton_review_2009} for more details on this strategy.

@@

@@

Unfortunately, the SSIM and PSNR metrics are not particularly illuminating. It
is easiest to see this by plotting PSNR and SSIM against total acquisition time,
which is shown in Fig.~\ref{fig:time_ssim_psnr}. There are several
inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of all the
raster scans, while the 8~Hz scan has the highest. Second, all of the 15\% CS
scans except the 8~Hz version have as good or better SSIM numbers than the
raster scans. It makes no sense for a CS scan at a 5~Hz rate to have better
quality than a raster scan at a 5~Hz rate. It is interesting to also compare
these numbers to the batch of 1~Hz raster scans we compared in
Section~\ref{sec:psnr_ssim_limits}. The blue shaded bands of
Figs~\ref{fig:time_ssim_psnr} indicate the mean of the SSIM and PSNR metrics
from Section \ref{sec:psnr_ssim_limits} plus or minus one standard deviation.
This seems to be further evidence that, at least for our experimental setup,
these numbers are not especially meaningful.

\begin{figure*}[h!]
  % \begin{subfigure}{1\textwidth}
  %   \includesvg[scale=1]{figures/cs_rast_time_vs_ssim_psnr.svg}
  %   \caption{(left) SSIM as a function of total acquisition time. (right) PSNR
  %     as a function of total acquisition time.}
  %   \label{fig:time_ssim_psnr}
  % \end{subfigure}

  % \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{figures/cs_rast_damage.svg}
    % \caption{(left) RDI as a function of scan rate for raster scans and CS scans
      % at 10\% and 15\% sampling. (right) RDI as a function of total imaging
      % time.}
  % \end{subfigure}
\caption{(left) RDI as a function of scan rate for raster scans and CS scans
      at 10\% and 15\% sampling. (right) RDI as a function of total imaging
      time.}
    \label{fig:time_damage}
  % \label{fig:time_vs_metrics}
\end{figure*}

@@

One final point that should be mentioned is that, by using an $X$-axis
controller designed for tracking step inputs, we have unfairly disadvantaged
raster scanning. Due the faster harmonic decay of a triangle wave compared to a
series of step inputs, in principle a higher bandwidth $X$-axis controller could
be used for raster scanning because the cross-coupling concerns discussed in
Section~\ref{sec:cz_cr_cs} would play a smaller role. While this will be
discussed a bit further in the next chapter, for now we note that the most
prominent way the lower bandwidth $X$-axis controller has limited raster
scanning is by chopping off the left and right edges of the images, which can be
seen in Fig.~\ref{fig:resultsF1_images} and \ref{fig:pixel_rows}. However, the
metrics are computed on a subslice that is large enough to eliminate this
region. Additionally, the RDI is mostly affected by the $Z$-direction bandwidth.

>>>>

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times.
\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[h!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    % 
    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}
     % 
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}
     % 
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}
     % 
    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
    %
    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}\\
    % 
    % ------------------------------ Row  2 --------------------------------------------
    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\todo{Re-do this figure???}
\endgroup

@@

The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
and inpainting, in which the first term seeks a sparse solution while the
last two terms try to diffuse pixel information.
\todo{When written this way, it seems that BP+VV/TV can could also be interpreted in the frameowrk of overcomplete dictionaries?\cite{candes_redundant_2011}. }
To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}
\end{equation*}
where
\begin{equation*}
W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T.
%   W = \begin{bmatrix}U^T\\\alpha_hD_h\\\alpha_vD_v \end{bmatrix}.
\end{equation*}

One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
\begin{equation}
  f_{\mu} = \max_{u\in Q_d} \left\langle u,
    W x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
\end{equation}
The gradient of \eqref{eqn:fcn_prox} is given by
\begin{equation*}
  \nabla f_{\mu}(x)[i] = W^Tu_{\mu}(x)
\end{equation*}
where
\begin{equation*}
  (u_{\mu}(x))[i] = 
\begin{cases}
    \mu^{-1}(Wx)[i], & |W x[i]| < \mu,\\
    \text{sgn}(W x[i]), & \text{else}.
  \end{cases}
\end{equation*}
The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.

\todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
\begin{algorithm}
  \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}

@@

@@

\begin{figure}[ht!]
  \includegraphics[width=1\columnwidth]{figures/exp_setup.pdf}
  \caption{Schematic diagram of the expermental AFM setup.}
  \label{fig:exp_setup}
\end{figure}

@@

All control logic is programmed using LabVIEW 2019 and compiled to a Xilinx
Spartan-6 LX150 Field Programmable Gate Array (FPGA) inside the cRIO-9082. The
cRIO includes a 16-Bit, 100 kHz NI-9215 analog-to-digital input module and a
16-Bit, 100 kHz NI-9263 digital-to-analog output module. All control loops are
implemented using a 25 kHz sampling rate.

% =========================================================================
\section{Control}\label{sec:control}
The control structure for each axis is different. For the $X$-axis, we use a
state space controller. It is described fully in \cite{braker_afmmpc_2019} and
achieves a bandwidth of about 150 Hz, which is over 1/3 of the first $X$-axis
resonance at 350 Hz.

@@

@@

For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency. We truncate this series such that the highest frequency is smaller than 200 Hz. See, e.g., \cite{clayton_review_2009} for more details on this strategy. Note that these scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning. On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.

@@

Unfortunately, the SSIM and PSNR metrics are not particularly illuminating. It
is easiest to see this by plotting PSNR and SSIM against total acquisition time,
which is shown in Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}. There are several
inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of all the
raster scans, while the 8~Hz scan has the highest. Second, all of the 15\% CS
scans except the 8~Hz version have as good or better SSIM numbers than the
raster scans. It makes no sense for a CS scan at a 5~Hz rate to have better
quality than a raster scan at a 5~Hz rate.

% It is interesting to also compare
% these numbers to the batch of 1~Hz raster scans we compared in
% Section~\ref{sec:limits}.
% The blue shaded bands of
% Figs~\ref{fig:time_ssim_psnr} indicate the mean of the SSIM and PSNR metrics
% from Section \ref{sec:psnr_ssim_limits} plus or minus one standard deviation.
% This seems to be further evidence that, at least for our experimental setup,
% these numbers are not especially meaningful.

\begin{figure*}[h!]
  \begin{subfigure}{0.33\textwidth}
    \includesvg[width=\textwidth]{figures/cs_rast_time_vs_ssim.svg}
    \caption{}
    \label{fig:time_ssim}
  \end{subfigure}
  \begin{subfigure}{0.33\textwidth}
    \includesvg[width=1\textwidth]{figures/cs_rast_time_vs_psnr.svg}
    \caption{}
    \label{fig:time_psnr}
  \end{subfigure}
  \begin{subfigure}{0.33\textwidth}
    \includesvg[width=\textwidth]{figures/cs_rast_damage.svg}
    \caption{}
    \label{fig:time_damage}
  \end{subfigure}
\caption{Metrics for raster scan and $\mu$-path scans at 10\% and 15\% sampling. (a) SSIM as a function of total acquisition time. (b) PSNR  as a function of total acquisition time. (c) RDI as a function of total acquisition time.}

  % \label{fig:time_vs_metrics}
\end{figure*}

@@
